Improved Bounds for Online Balanced Repartitioning

### 2020-04-02 paper/paper.tex
On cascade

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
    \rowcolor{gray!50}
    \textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
      \textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 3\hspace{0.3cm}(\S 9.3) \\ 
      \rowcolor{gray!25}
      \textbf{$k=3$}&  $27\cdot \ell $\hspace{0.3cm}(\S 9.3)& $O(\ell)$\hspace{0.3cm}(\S 9.3)\\
      \textbf{$\ell=2$}&  $2k-1$\hspace{0.3cm}(\S 9.3)&\hspace{0.3cm}$O(k^2)$\hspace{0.3cm}\cite{repartition-disc}\\
      \rowcolor{gray!25}
      $\ell \geq 3$& $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S 9.3)&$O(k^2 \cdot \ell^2)$\hspace{0.3cm}\cite{repartition-disc} \\
      Perfect partition & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S 9.3)&$O(k \cdot \ell)$\hspace{0.3cm} (\S 9) \\
    \end{tabular}
                \caption{Overview of the results. Most specific cases are tight. The general case still has a significant gap between the lower bound and the upper bound. If either $k$ or $\ell$ is missing from a variant description, it is assumed to be arbitrary.
                  }
  \label{tab:overview}
  \vspace{-7mm}
\end{table*}

@@

\begin{theorem}
  A single repartition of DET2 migrates nodes among at most $p(k)^2+k$ clusters, where $p(k)$ is the number of integer partitions $k$.
  The corollary is, the cost of the repartition is bounded by $O(k \cdot \alpha \cdot e^{c\cdot \sqrt{k}})$ for a constant $c$.
\end{theorem}

@@

  Consider a repartition from a perspective of a single cluster.
  Prior to the repartition, it had a signature $S^-(C)$, and after the repartition it has a signature $S^+(C)$.
\end{proof}

>>>>

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
    \rowcolor{gray!50}
    \textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
      \textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & TBD\hspace{0.3cm}(\S 9.3) \\ 
      \rowcolor{gray!25}
      \textbf{$k=3$}&  $27\cdot \ell $\hspace{0.3cm}(\S 9.3)& $O(\ell)$\hspace{0.3cm}(\S 9.3)\\
      \textbf{$\ell=2$}&  $k+1 = \Omega(k)$\hspace{0.3cm}(\S 9.3)&\hspace{0.3cm}$O(k^2)$\hspace{0.3cm}\cite{repartition-disc}\\
      \rowcolor{gray!25}
      $\ell \geq 3$& $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S 9.3)&$O(k^2 \cdot \ell^2)$\hspace{0.3cm}\cite{repartition-disc} \\
      Perfect partition & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S 9.3)&$O(k \cdot \ell)$\hspace{0.3cm} (\S 9) \\
    \end{tabular}
                \caption{Overview of the results. Most specific cases are tight. The general case still has a significant gap between the lower bound and the upper bound. If either $k$ or $\ell$ is missing from a variant description, it is assumed to be arbitrary.
                  }
  \label{tab:overview}
  \vspace{-7mm}
\end{table*}

@@

\begin{theorem}
  A single repartition of DET2 migrates nodes among at most $p(k)^2+(k+1)$ clusters, where $p(k)$ is the number of integer partitions $k$.
  The corollary is, the cost of the repartition is bounded by $O(k \cdot \alpha \cdot e^{c\cdot \sqrt{k}})$ for a constant $c$.
\end{theorem}

@@

  Fix a repartition.

  Consider the repartition from the perspective of a single cluster.
  Prior to the repartition, it had a signature $S^-(C)$, and after the repartition it has a signature $S^+(C)$.

  Now we construct a graph $G$ of component exchange among clusters.
  The vertices are the clusters.
  If a pair of clusters $C_1, C_2$ exchange components during the repartition, we produce an edge and we label it with the \emph{signature of exchange}, i.e., a pair of cluster signatures (both ways), limited to the exchanged clusters between $C_1,C_2$ only (i.e., not necessarily summing to $k$, and  note that also not necessarily having the same size!).

  Proof by contradiction.
  Assume that there exists a component in $G$ of size greater than $p(k)^2+(k+1)$.

\end{proof}
